Trends of SDR in Thessaloniki

### 2023-06-14 Article.Rmd
Commit 2023-06-14 12:17

```{r szatrends, echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('Trend distribution for all-sky conditions.', 'Trend distribution for cloud-sky conditions.'), out.width='.30\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics("./images/SzaTrends-13.pdf")
cat(" space ")     
knitr::include_graphics("./images/SzaTrends-21.pdf")
```

```{r szatrends2, results="asis", echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('Trend distribution for all-sky conditions.', 'Trend distribution for cloud-sky conditions.'), out.width='.30\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics("./images/SzaTrends-13.pdf")
cat("\\ \n")     
knitr::include_graphics("./images/SzaTrends-21.pdf")
```

>>>>

```{r szatrends, echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('Trend distribution for all-sky conditions.', 'Trend distribution for cloud-sky conditions.'), out.width='.33\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics("./images/SzaTrends-13.pdf")
knitr::include_graphics("./images/SzaTrends-21.pdf")
```

```{r szatrends2, results="asis", echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA.', fig.subcap=c('Trend distribution for all-sky conditions.', 'Trend distribution for cloud-sky conditions.'), out.width='.30\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics("./images/SzaTrends-13.pdf")
cat("\\ \\ \n")     
knitr::include_graphics("./images/SzaTrends-21.pdf")
```
